Hospital Information Technology and Physician Response

### 2021-10-14 Presentations/ReadingGroupPres.tex

\section{Model and Data}

@@

Measures of physician labor market behavior
\begin{itemize}
    \item Number/percent of shared patients physician $i$ has with hospital $h$: \underline{CMS Shared Patient Data} (2009-2015)
    \item Total Part B claims for physician $i$: \underline{Medicare Provider Utilization and Payment Data} (starts in 2012)
\end{itemize}
\end{frame}

\begin{frame}[noframenumbering]{Data}
\begin{equation*}
    p_{iht}=f(\textcolor{blue}{EHR_{ht},EHR_{-h,t}},X_i,H_{jt},...)
\end{equation*}

@@

\begin{frame}[noframenumbering]{Data}
\begin{equation*}
    p_{iht}=f(EHR_{ht},EHR_{-h,t},\textcolor{blue}{X_i},H_{jt},...)
\end{equation*}

@@

\begin{frame}[noframenumbering]{Data}
\begin{equation*}
    p_{iht}=f(EHR_{ht},EHR_{-h,t},X_i,\textcolor{blue}{H_{jt}},...)
\end{equation*}

@@

    \item My idea is to estimate these two separately, but there are issues because of spillover effects (if hospital $-h$ implements an EHR)

>>>>

\section{Data}

@@

Measures of physician labor market behavior
\begin{itemize}
    \item Number/percent of shared patients physician $i$ has with hospital $h$: \underline{CMS Shared Patient Data} (2009-2015)
    \begin{itemize}
        \item Main dataset: physician hospital level panel
        \item Physicians and hospitals in this data work closely together, likely the physician works \textit{in} the hospital
    \end{itemize}
    \item Total Part B claims for physician $i$: \underline{Medicare Provider Utilization and Payment Data} (starts in 2012)
\end{itemize}
\end{frame}

\begin{frame}{Data}
\begin{equation*}
    p_{iht}=f(\textcolor{blue}{EHR_{ht},EHR_{-h,t}},X_i,H_{jt},...)
\end{equation*}

@@

\begin{frame}{Data}
\begin{equation*}
    p_{iht}=f(EHR_{ht},EHR_{-h,t},\textcolor{blue}{X_i},H_{jt},...)
\end{equation*}

@@

\begin{frame}{Data}
\begin{equation*}
    p_{iht}=f(EHR_{ht},EHR_{-h,t},X_i,\textcolor{blue}{H_{jt}},...)
\end{equation*}

@@

    \item My idea is to estimate these two separately, but there are issues because of spillover effects (hospital $-h$ implements an EHR)
